Looking at Non-Linear Dimension Reductions as Models in the Data Space

### 2024-08-22 paper.qmd
Updated the scaling function

  # Step 2: Calculate the range of each dimension
  ranges <- apply(data_centered, 2, function(x) max(x) - min(x))

  # Step 3: Find the dimension with the largest range
  max_range <- max(ranges)
  scaled_data <- data_centered

  # Step 4: Scale each dimension
  for (i in seq_along(ranges)) {
    scaling_factor <- ranges[i] / max_range
    scaled_data[, i] <- data_centered[, i] / ranges[i] * scaling_factor
  }

  # Step 5: Rescale the dimension with the largest range to [-1, 1]
  largest_dim_index <- which.max(ranges)
  scaled_data[, largest_dim_index] <- scaled_data[, largest_dim_index] * max_range

  return(scaled_data)
}
```

>>>>

  # Step 2: Calculate the standard deviation of each dimension
  sds <- apply(data_centered, 2, sd)

  # Step 3: Scale each dimension to have the range [0, 1]
  data_scaled <- apply(data_centered, 2, function(col) col / max(abs(col)))

  # Step 4: Scale dimensions according to their variation
  # The dimension with the highest standard deviation is scaled to [-1, 1]
  # Other dimensions are scaled to smaller ranges based on their standard deviations
  max_sd <- max(sds)

  # Normalize the standard deviations to get scaling factors
  scaling_factors <- sds / max_sd

  for (i in seq_along(scaling_factors)) {
    data_scaled[, i] <- data_scaled[, i] * scaling_factors[i]
  }

  return(data_scaled)
}
```
